CLT Results

### 2022-04-13 analysis/clt_irt_analysis.Rmd
add model params

```{r}
iic2 <- posterior_samples(irt2)%>% 
  select(b_eta_Intercept, b_logalpha_Intercept, starts_with("r_targetWord"))%>%
  mutate(iter = 1:n()) %>% 
  pivot_longer(starts_with("r_targetWord")) %>%
  mutate(item      = str_extract(name, pattern = "(?<=\\[).*(?=,Intercept\\])"),
         parameter = ifelse(str_detect(name, "eta"), "xi", "logalpha"))%>%
  select(-name) %>% 
  pivot_wider(names_from = parameter, values_from = value)%>% 
  expand(nesting(iter, b_eta_Intercept, b_logalpha_Intercept, item, xi, logalpha),
         theta = seq(from = -6, to = 6, length.out = 100)) %>% 
  # note the difference in the equation
  mutate(p = inv_logit_scaled(exp(b_logalpha_Intercept + logalpha) * (b_eta_Intercept + theta + xi)))%>%
  mutate(i = p * (1 - p)) %>% 
  group_by(theta, item) %>% 
  summarise(i = median(i))%>%
  left_join(aoa%>%rename(item = targetWord))
```

@@

@@

```{r}
iic3 <- posterior_samples(irt3)%>% 
  select(b_eta_Intercept, b_logalpha_Intercept, starts_with("r_targetWord"))%>%
  mutate(iter = 1:n()) %>% 
  pivot_longer(starts_with("r_targetWord")) %>%
  mutate(item      = str_extract(name, pattern = "(?<=\\[).*(?=,Intercept\\])"),
         parameter = ifelse(str_detect(name, "eta"), "xi", "logalpha"))%>%
  select(-name) %>% 
  pivot_wider(names_from = parameter, values_from = value)%>% 
  expand(nesting(iter, b_eta_Intercept, b_logalpha_Intercept, item, xi, logalpha),
         theta = seq(from = -6, to = 6, length.out = 100)) %>% 
  # note the difference in the equation
  mutate(p = inv_logit_scaled(exp(b_logalpha_Intercept + logalpha) * (b_eta_Intercept + theta + xi)))%>%
  mutate(i = p * (1 - p)) %>% 
  group_by(theta, item) %>% 
  summarise(i = median(i))%>%
  left_join(aoa%>%rename(item = targetWord))
```

>>>>

```{r}
iic2 <- posterior_samples(irt2)%>% 
  select(b_eta_Intercept, b_logalpha_Intercept, starts_with("r_targetWord"))%>%
  mutate(iter = 1:n()) %>% 
  pivot_longer(starts_with("r_targetWord")) %>%
  mutate(item      = str_extract(name, pattern = "(?<=\\[).*(?=,Intercept\\])"),
         parameter = ifelse(str_detect(name, "eta"), "xi", "logalpha"))%>%
  select(-name) %>% 
  pivot_wider(names_from = parameter, values_from = value)%>% 
  expand(nesting(iter, b_eta_Intercept, b_logalpha_Intercept, item, xi, logalpha),
         theta = seq(from = -6, to = 6, length.out = 100)) %>% 
  # note the difference in the equation
 # mutate(p = inv_logit_scaled(exp(b_logalpha_Intercept + logalpha) * (b_eta_Intercept + theta + xi)))%>%
  #mutate(i = p * (1 - p)) %>% 
  mutate(i = (exp(b_logalpha_Intercept + logalpha))^2 *inv_logit_scaled(b_eta_Intercept + theta + xi)*(1-inv_logit_scaled(b_eta_Intercept + theta + xi))) %>% 
  group_by(theta, item) %>% 
  summarise(i = median(i))%>%
  left_join(aoa%>%rename(item = targetWord))
```

@@

write_csv(params,"../data/model_parameters_3PL.csv")

@@

```{r}
iic3 <- posterior_samples(irt3)%>% 
  select(b_eta_Intercept, b_logalpha_Intercept, starts_with("r_targetWord"))%>%
  mutate(iter = 1:n()) %>% 
  pivot_longer(starts_with("r_targetWord")) %>%
  mutate(item      = str_extract(name, pattern = "(?<=\\[).*(?=,Intercept\\])"),
         parameter = ifelse(str_detect(name, "eta"), "xi", "logalpha"))%>%
  select(-name) %>% 
  pivot_wider(names_from = parameter, values_from = value)%>% 
  expand(nesting(iter, b_eta_Intercept, b_logalpha_Intercept, item, xi, logalpha),
         theta = seq(from = -6, to = 6, length.out = 100)) %>% 
  # note the difference in the equation
  #mutate(p = 0.25 + 0.75*inv_logit_scaled(exp(b_logalpha_Intercept + logalpha) * (b_eta_Intercept + theta + xi)))%>%
  #mutate(i = p * (1 - p)) %>% 
  mutate(i = (exp(b_logalpha_Intercept + logalpha))^2 *
           ((1-inv_logit_scaled(b_eta_Intercept + theta + xi))/(inv_logit_scaled(b_eta_Intercept + theta + xi)))*
           ((inv_logit_scaled(b_eta_Intercept + theta + xi)-0.25)/(1-0.25))^2)%>%
  group_by(theta, item) %>% 
  summarise(i = median(i))%>%
  left_join(aoa%>%rename(item = targetWord))
```
